% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
  12pt,
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot{}
\fancyhead[L]{APCs and Author Diversity (Supplement)}
\fancyhead[R]{p. \thepage}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{caption}
\DeclareCaptionLabelFormat{Sformat}{#1 S#2}
\captionsetup[table]{labelformat=Sformat}
\captionsetup[figure]{labelformat=Sformat}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Appendix to Edge Effects MS},
  pdfauthor={Parsons and Bruna},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Appendix to Edge Effects MS}
\author{Parsons and Bruna}
\date{}

\begin{document}
\maketitle

Draft: 12 June 2025

The following articles were used in the review.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-aragonEdgeTypeDetermines2015}
Aragón, Gregorio, Laura Abuja, Rocío Belinchón, and Isabel Martínez.
2015. {``Edge Type Determines the Intensity of Forest Edge Effect on
Epiphytic Communities.''} \emph{European Journal of Forest Research} 134
(3): 443--51. \url{https://doi.org/10.1007/s10342-015-0863-5}.

\bibitem[\citeproctext]{ref-badanoMicroclimateSeedingPredation2015}
Badano, Ernesto I., Omar R. Samour-Nieva, Joel Flores, and David
Douterlungne. 2015. {``Microclimate and Seeding Predation as Drivers of
Tree Recruitment in Human-Disturbed Oak Forests.''} \emph{Forest Ecology
and Management} 356 (November): 93--100.
\url{https://doi.org/10.1016/j.foreco.2015.07.031}.

\bibitem[\citeproctext]{ref-bakerMicroclimaticEdgeEffects2016}
Baker, Thomas P., Gregory J. Jordan, and Susan C. Baker. 2016.
{``Microclimatic Edge Effects in a Recently Harvested Forest: {Do}
Remnant Forest Patches Create the Same Impact as Large Forest Areas?''}
\emph{Forest Ecology and Management} 365 (April): 128--36.
\url{https://doi.org/10.1016/j.foreco.2016.01.022}.

\bibitem[\citeproctext]{ref-bakerMicroclimateSpaceTime2014}
Baker, Thomas P., Gregory J. Jordan, E. Ashley Steel, Nicholas M.
Fountain-Jones, Timothy J. Wardlaw, and Susan C. Baker. 2014.
{``Microclimate Through Space and Time: {Microclimatic} Variation at the
Edge of Regeneration Forests over Daily, Yearly and Decadal Time
Scales.''} \emph{Forest Ecology and Management} 334 (December): 174--84.
\url{https://doi.org/10.1016/j.foreco.2014.09.008}.

\bibitem[\citeproctext]{ref-brigicOldForestEdges2014}
Brigić, Andreja, Marija Starčević, Boris Hrašovec, and Zoltán Elek.
2014. {``Old Forest Edges May Promote the Distribution of Forest Species
in Carabid Assemblages ({Coleoptera}: {Carabidae}) in {Croatian}
Forests.''} \emph{European Journal of Entomology} 111 (5): 715--25.
\url{https://doi.org/10.14411/eje.2014.090}.

\bibitem[\citeproctext]{ref-brunaEdgeEffectsGrowth2011}
Bruna, Emilio M., and Ana Segalin De Andrade. 2011. {``Edge Effects on
Growth and Biomass Partitioning of an {Amazonian} Understory Herb (
\emph{{Heliconia} Acuminata} ; {Heliconiaceae}).''} \emph{American
Journal of Botany} 98 (10): 1727--34.
\url{https://doi.org/10.3732/ajb.1000290}.

\bibitem[\citeproctext]{ref-brunialtiFragmentationMediterraneanOak2012}
Brunialti, Giorgio, Luisa Frati, and Stefano Loppi. 2012.
{``Fragmentation of {Mediterranean} Oak Forests Affects the Diversity of
Epiphytic Lichens.''} \emph{Nova Hedwigia} 96 (1-2): 265--78.
\url{https://doi.org/10.1127/0029-5035/2012/0075}.

\bibitem[\citeproctext]{ref-buenoFacilitationEdgeEffects2015}
Bueno, Andrea, and Luis D. Llambí. 2015. {``Facilitation and Edge
Effects Influence Vegetation Regeneration in Old-Fields at the Tropical
{Andean} Forest Line.''} Edited by Karsten Wesche. \emph{Applied
Vegetation Science} 18 (4): 613--23.
\url{https://doi.org/10.1111/avsc.12186}.

\bibitem[\citeproctext]{ref-cadenassoFunctionalLocationForest1997}
Cadenasso, M L, M M Traynor, and S TA Pickett. 1997. {``Functional
Location of Forest Edges: Gradients of Multiple Physical Factors''} 27.

\bibitem[\citeproctext]{ref-camargoComplexEdgeEffects1995}
Camargo, J. L. C., and V. Kapos. 1995. {``Complex {Edge} {Effects} on
{Soil} {Moisture} and {Microclimate} in {Central} {Amazonian}
{Forest}.''} \emph{Journal of Tropical Ecology} 11 (2): 205--21.
\url{http://www.jstor.org/stable/2560108}.

\bibitem[\citeproctext]{ref-cappelattiSPATIALDISTRIBUTIONPOPULATION2015}
Cappelatti, Laura, and Jairo Lizandro Schmitt. 2015. {``{SPATIAL}
{DISTRIBUTION} {AND} {POPULATION} {STRUCTURE} {OF} {PALMS} ({ARECACEAE})
{IN} {A} {FOREST} {FRAGMENT} {OF} {LOWLAND} {DENSE} {HUMID} {FOREST}
{IN} {SOUTH} {BRAZIL}.''} \emph{Ciência Florestal} 25 (4): 817--25.
\url{https://doi.org/10.5902/1980509820577}.

\bibitem[\citeproctext]{ref-cerbonciniEdgeEffectsHabitat2016}
Cerboncini, Ricardo A. S., James J. Roper, and Fernando C. Passos. 2016.
{``Edge Effects Without Habitat Fragmentation? {Small} Mammals and a
Railway in the {Atlantic} {Forest} of Southern {Brazil}.''} \emph{Oryx}
50 (3): 460--67. \url{https://doi.org/10.1017/S0030605314001070}.

\bibitem[\citeproctext]{ref-chenContrastingMicroclimatesClearcut1993}
Chen, Jiquan, Jerry F. Franklin, and Thomas A. Spies. 1993.
{``Contrasting Microclimates Among Clearcut, Edge, and Interior of
Old-Growth {Douglas}-Fir Forest.''} \emph{Agricultural and Forest
Meteorology} 63 (3-4): 219--37.
\url{https://doi.org/10.1016/0168-1923(93)90061-L}.

\bibitem[\citeproctext]{ref-chenGrowingSeasonMicroclimaticGradients1995}
---------. 1995. {``Growing-{Season} {Microclimatic} {Gradients} from
{Clearcut} {Edges} into {Old}-{Growth} {Douglas}-{Fir} {Forests}.''}
\emph{Ecological Applications} 5 (1): 74--86.
\url{https://doi.org/10.2307/1942053}.

\bibitem[\citeproctext]{ref-christianiniEdgeEffectsDecrease2013}
Christianini, Alexander V., and Paulo S. Oliveira. 2013. {``Edge Effects
Decrease Ant-Derived Benefits to Seedlings in a Neotropical Savanna.''}
\emph{Arthropod-Plant Interactions} 7 (2): 191--99.
\url{https://doi.org/10.1007/s11829-012-9229-9}.

\bibitem[\citeproctext]{ref-crockattEdgeEffectsMoisture2015}
Crockatt, Martha E., and Daniel P. Bebber. 2015. {``Edge Effects on
Moisture Reduce Wood Decomposition Rate in a Temperate Forest.''}
\emph{Global Change Biology} 21 (2): 698--707.
\url{https://doi.org/10.1111/gcb.12676}.

\bibitem[\citeproctext]{ref-cubidesAnthropogenicDisturbanceEdge2011}
Cubides, Paola Johanna Isaacs, and José Nicolás Urbina Cardona. 2011.
{``Anthropogenic {Disturbance} and {Edge} {Effects} on {Anuran}
{Assemblages} {Inhabiting} {Cloud} {Forest} {Fragments} in
{Colombia}.''} \emph{Natureza \& Conservação} 9 (1): 39--46.
\url{https://doi.org/10.4322/natcon.2011.004}.

\bibitem[\citeproctext]{ref-davies-colleyMicroclimateGradientsForest2000}
Davies-Colley, R J, and G W Payne. 2000. {``Microclimate Gradients
Across a Forest Edge.''} \emph{NEW ZEALAND JOURNAL OF ECOLOGY} 24 (2).

\bibitem[\citeproctext]{ref-delgadoEdgeEffectsRoads2007}
Delgado, Juan D., Natalia L. Arroyo, José R. Arévalo, and José M.
Fernández-Palacios. 2007. {``Edge Effects of Roads on Temperature,
Light, Canopy Cover, and Canopy Height in Laurel and Pine Forests
({Tenerife}, {Canary} {Islands}).''} \emph{Landscape and Urban Planning}
81 (4): 328--40.
\url{https://doi.org/10.1016/j.landurbplan.2007.01.005}.

\bibitem[\citeproctext]{ref-didhamEdgeEffectsDisrupt2014a}
Didham, Raphael K., and Robert M. Ewers. 2014. {``Edge {Effects}
{Disrupt} {Vertical} {Stratification} of {Microclimate} in a {Temperate}
{Forest} {Canopy}.''} \emph{Pacific Science} 68 (4): 493--508.
\url{https://doi.org/10.2984/68.4.4}.

\bibitem[\citeproctext]{ref-didhamEdgeStructureDetermines1999a}
Didham, Raphael K., and John H. Lawton. 1999. {``Edge {Structure}
{Determines} the {Magnitude} of {Changes} in {Microclimate} and
{Vegetation} {Structure} in {Tropical} {Forest} {Fragments}.''}
\emph{Biotropica} 31 (1): 17. \url{https://doi.org/10.2307/2663956}.

\bibitem[\citeproctext]{ref-dilrukshiKirigalaForestFragments2016}
Dilrukshi, Iadn, and Smw Ranwala. 2016. {``Kirigala Forest Fragments and
the Identity as a Dipterocarp Plantation or {Hora} {Kele} of
{Ingiriya}.''} \emph{Journal of the National Science Foundation of Sri
Lanka} 44 (3): 313. \url{https://doi.org/10.4038/jnsfsr.v44i3.8012}.

\bibitem[\citeproctext]{ref-dodonovRoleEdgeContrast2013}
Dodonov, Pavel, Karen A. Harper, and Dalva M. Silva-Matos. 2013. {``The
Role of Edge Contrast and Forest Structure in Edge Influence: Vegetation
and Microclimate at Edges in the {Brazilian} Cerrado.''} \emph{Plant
Ecology} 214 (11): 1345--59. \url{http://www.jstor.org/stable/24553703}.

\bibitem[\citeproctext]{ref-dovciakSecondaryEdgeEffects2014}
Dovčiak, Martin, and Jordan Brown. 2014. {``Secondary Edge Effects in
Regenerating Forest Landscapes: Vegetation and Microclimate Patterns and
Their Implications for Management and Conservation.''} \emph{New
Forests} 45 (5): 733--44.
\url{https://doi.org/10.1007/s11056-014-9419-7}.

\bibitem[\citeproctext]{ref-draaijersAtmosphericDepositionComplex1994}
Draaijers, G. P. J., R. Van Ek, and W. Bleuten. 1994. {``Atmospheric
Deposition in Complex Forest Landscapes.''} \emph{Boundary-Layer
Meteorology} 69 (4): 343--66. \url{https://doi.org/10.1007/BF00718124}.

\bibitem[\citeproctext]{ref-ewersFragmentationImpairsMicroclimate2013a}
Ewers, Robert M., and Cristina Banks-Leite. 2013. {``Fragmentation
{Impairs} the {Microclimate} {Buffering} {Effect} of {Tropical}
{Forests}.''} Edited by Gil Bohrer. \emph{PLoS ONE} 8 (3): e58093.
\url{https://doi.org/10.1371/journal.pone.0058093}.

\bibitem[\citeproctext]{ref-gehlhausenVegetationMicroclimaticEdge2000}
Gehlhausen, Sophia M., Mark W. Schwartz, and Carol K. Augspurger. 2000.
{``Vegetation and {Microclimatic} {Edge} {Effects} in {Two}
{Mixed}-{Mesophytic} {Forest} {Fragments}.''} \emph{Plant Ecology} 147
(1): 21--35. \url{http://www.jstor.org/stable/20050900}.

\bibitem[\citeproctext]{ref-gignacEffectsFragmentSize2005}
Gignac, L. Dennis, and Mark R. T. Dale. 2005. {``Effects of {Fragment}
{Size} and {Habitat} {Heterogeneity} on {Cryptogam} {Diversity} in the
{Low}-Boreal {Forest} of {Western} {Canada}.''} \emph{The Bryologist}
108 (1): 50--66.
\url{https://doi.org/10.1639/0007-2745(2005)108\%5B50:EOFSAH\%5D2.0.CO;2}.

\bibitem[\citeproctext]{ref-heitheckerEdgerelatedGradientsMicroclimate2007}
Heithecker, Troy D., and Charles B. Halpern. 2007. {``Edge-Related
Gradients in Microclimate in Forest Aggregates Following Structural
Retention Harvests in Western {Washington}.''} \emph{Forest Ecology and
Management} 248 (3): 163--73.
\url{https://doi.org/10.1016/j.foreco.2007.05.003}.

\bibitem[\citeproctext]{ref-hennenbergDetectionSeasonalVariability2008}
Hennenberg, Klaus Josef, Dethardt Goetze, Jörg Szarzynski, Bettina
Orthmann, Björn Reineking, Ingo Steinke, and Stefan Porembski. 2008.
{``Detection of Seasonal Variability in Microclimatic Borders and
Ecotones Between Forest and Savanna.''} \emph{Basic and Applied Ecology}
9 (3): 275--85. \url{https://doi.org/10.1016/j.baae.2007.02.004}.

\bibitem[\citeproctext]{ref-ibanezSharpTransitionsMicroclimatic2013}
Ibanez, Thomas, Christelle Hély, and Cédric Gaucherel. 2013. {``Sharp
Transitions in Microclimatic Conditions Between Savanna and Forest in
{New} {Caledonia}: {Insights} into the Vulnerability of Forest Edges to
Fire: {Microclimate} at the {Forest} {Edge}.''} \emph{Austral Ecology}
38 (6): 680--87. \url{https://doi.org/10.1111/aec.12015}.

\bibitem[\citeproctext]{ref-joseVegetationResponsesEdgetointerior1996}
Jose, Shibu, Andrew R. Gillespie, Suman Jacob George, and B.Mohan Kumar.
1996. {``Vegetation Responses Along Edge-to-Interior Gradients in a High
Altitude Tropical Forest in Peninsular {India}.''} \emph{Forest Ecology
and Management} 87 (1-3): 51--62.
\url{https://doi.org/10.1016/S0378-1127(96)03836-4}.

\bibitem[\citeproctext]{ref-kapos1997edge}
Kapos, V. 1997. {``Edge-Related Changes in Environment and Plant
Responses Due to Forest Fragmentation in Central {Amazonia}.''}
\emph{Tropical Forest Remnants: Ecology, Management, and Conservation of
Fragmented Communities}.

\bibitem[\citeproctext]{ref-kunertHigherTreeTranspiration2015}
Kunert, Norbert, Luiza Maria Teóphilo Aparecido, Niro Higuchi, Joaquim
Dos Santos, and Susan Trumbore. 2015. {``Higher Tree Transpiration Due
to Road-Associated Edge Effects in a Tropical Moist Lowland Forest.''}
\emph{Agricultural and Forest Meteorology} 213 (November): 183--92.
\url{https://doi.org/10.1016/j.agrformet.2015.06.009}.

\bibitem[\citeproctext]{ref-lehtinenEdgeEffectsExtinction}
Lehtinen, Richard M, Jean-Baptiste Ramanamanjato, and Joe Gaby
Raveloarison. n.d. {``Edge Effects and Extinction Proneness in a
Herpetofauna from {Madagascar}.''}

\bibitem[\citeproctext]{ref-lima-ribeiroEfeitosBordaSobre2008}
Lima-Ribeiro, Matheus De Souza. 2008. {``Efeitos de Borda Sobre a
Vegetação e Estruturação Populacional Em Fragmentos de {Cerradão} No
{Sudoeste} {Goiano}, {Brasil}.''} \emph{Acta Botanica Brasilica} 22 (2):
535--45. \url{https://doi.org/10.1590/S0102-33062008000200020}.

\bibitem[\citeproctext]{ref-macdougallUnderstoreyLightRegime1992}
MacDougall, Andrew, and Martin Kellman. 1992. {``The {Understorey}
{Light} {Regime} and {Patterns} of {Tree} {Seedlings} in {Tropical}
{Riparian} {Forest} {Patches}.''} \emph{Journal of Biogeography} 19 (6):
667. \url{https://doi.org/10.2307/2845708}.

\bibitem[\citeproctext]{ref-magnagoMicroclimaticConditionsForest2015}
Magnago, Luiz Fernando Silva, Mariana Ferreira Rocha, Leila Meyer,
Sebastião Venâncio Martins, and João Augusto Alves Meira-Neto. 2015.
{``Microclimatic Conditions at Forest Edges Have Significant Impacts on
Vegetation Structure in Large {Atlantic} Forest Fragments.''}
\emph{Biodiversity and Conservation} 24 (9): 2305--18.
\url{https://doi.org/10.1007/s10531-015-0961-1}.

\bibitem[\citeproctext]{ref-malombeEdgeEffectEpiphyllous2016}
Malombe, Itambo, Kennedy Wambua Matheka, Tamás Pócs, and Jairo Patiño.
2016. {``Edge Effect on Epiphyllous Bryophytes in {Taita} {Hills}
Fragmented Afromontane Forests.''} \emph{Journal of Bryology} 38 (1):
33--46. \url{https://doi.org/10.1179/1743282015Y.0000000015}.

\bibitem[\citeproctext]{ref-martiniMicroclimaConfortoTermico2015}
Martini, Angeline, and Daniela Biondi. 2015. {``Microclima e {Conforto}
{Térmico} de Um {Fragmento} de {Floresta} {Urbana} Em {Curitiba},
{PR}.''} \emph{Floresta e Ambiente} 22 (2): 182--93.
\url{https://doi.org/10.1590/2179-8087.082114}.

\bibitem[\citeproctext]{ref-matlackMicroenvironmentVariationForest1993}
Matlack, Glenn R. 1993. {``Microenvironment Variation Within and Among
Forest Edge Sites in the Eastern {United} {States}.''} \emph{Biological
Conservation} 66 (3): 185--94.
\url{https://doi.org/10.1016/0006-3207(93)90004-K}.

\bibitem[\citeproctext]{ref-mendoncaEdgeEffectsSavanna2015}
Mendonça, Augusto H., Cibele Russo, Antônio C. G. Melo, and Giselda
Durigan. 2015. {``Edge Effects in Savanna Fragments: A Case Study in the
Cerrado.''} \emph{Plant Ecology \& Diversity} 8 (4): 493--503.
\url{https://doi.org/10.1080/17550874.2015.1014068}.

\bibitem[\citeproctext]{ref-do2010eficacia}
Nascimento, Marcio Irias do, Fábio Poggiani, Giselda Durigan, Antonio
Francisco Iemma, and Demóstenes Ferreira da Silva Filho. 2010.
{``Eficácia de Barreira de Eucaliptos Na Contenção Do Efeito de Borda Em
Fragmento de Floresta Subtropical No Estado de {São} {Paulo}, {Brasil}
{The} Effectiveness of {Eucalyptus} Barrier in Containing the Edge
Effect on a Subtropical Forest Fragment in the State of {São} {Paulo},
{Brazil}.''} \emph{Scientia Florestalis} 38: 191--203.

\bibitem[\citeproctext]{ref-newmarkTanzanianForestEdge}
Newmark, William D. n.d. {``Tanzanian {Forest} {Edge} {Microclimatic}
{Gradients}: {Dynamic} {Patterns}.''}

\bibitem[\citeproctext]{ref-pedroso-de-moraesEdgeEffectOrchids}
Pedroso-de-Moraes, Cristiano, Lígia Eleonor Prezzi, Thiago de
Souza-Leal, Thiago Fernandes Canonici, Olavo Raymundo Jr, and Paulo
Silveira. n.d. {``Edge {Effect} on {Orchids} of a {Fragment} of
{Semi}-{Deciduous} {Seasonal} {Forest} in the {Southeast} of
{Brazil}.''}

\bibitem[\citeproctext]{ref-pereira2014edge}
Pereira, AF de N, IAA da Silva, ACP Santiago, ICL Barros, et al. 2014.
{``Edge Effects on Fern Community in an {Atlantic} {Forest} Remnant
({Bonito}, {Pernambuco}, {Brazil}).''} \emph{Interciencia} 39 (4):
281--87.

\bibitem[\citeproctext]{ref-pinheiro2013annual}
Pinheiro, Marayana Prado, Josafá Amaral de Oliveira Filho, Solange
França, André Márcio Amorim, and Marcelo Schramm Mielke. 2013. {``Annual
Variation in Canopy Openness, Air Temperature and Humidity in the
Understory of Three Forested Sites in Southern {Bahia} {State},
{Brazil}.''} \emph{Ciência Florestal} 23: 107--16.

\bibitem[\citeproctext]{ref-pintoLandscapeAttributesDrive2010}
Pinto, Severino R. R., Gabriel Mendes, André M. M. Santos, Mateus
Dantas, Marcelo Tabarelli, and Felipe P. L. Melo. 2010. {``Landscape
{Attributes} {Drive} {Complex} {Spatial} {Microclimate} {Configuration}
of {Brazilian} {Atlantic} {Forest} {Fragments}.''} \emph{Tropical
Conservation Science} 3 (4): 389--402.
\url{https://doi.org/10.1177/194008291000300404}.

\bibitem[\citeproctext]{ref-pohlmanEdgeEffectsLinear2007}
Pohlman, Catherine L., Stephen M. Turton, and Miriam Goosem. 2007.
{``Edge {Effects} of {Linear} {Canopy} {Openings} on {Tropical} {Rain}
{Forest} {Understory} {Microclimate}.''} \emph{Biotropica} 39 (1):
62--71. \url{http://www.jstor.org/stable/30045485}.

\bibitem[\citeproctext]{ref-pohlmanTemporalVariationMicroclimatic2009}
---------. 2009. {``Temporal Variation in Microclimatic Edge Effects
Near Powerlines, Highways and Streams in {Australian} Tropical
Rainforest.''} \emph{Agricultural and Forest Meteorology} 149 (1):
84--95. \url{https://doi.org/10.1016/j.agrformet.2008.07.003}.

\bibitem[\citeproctext]{ref-rajpar2015bird}
Rajpar, MN, and M Zakaria. 2015. {``Bird Abundance and Its Relationship
with Microclimate and Habitat Variables in Open-Area and Shrub Habitats
in {Selangor}, {Peninsular} {Malaysia}.''} \emph{JAPS: Journal of Animal
\& Plant Sciences} 25 (1).

\bibitem[\citeproctext]{ref-ramosMicroclimateAtlanticForest2006}
Ramos, Flavio Nunes, and Flavio Antonio Maës Santos. 2006.
{``Microclimate of {Atlantic} Forest Fragments: Regional and Local Scale
Heterogeneity.''} \emph{Brazilian Archives of Biology and Technology} 49
(6): 935--44. \url{https://doi.org/10.1590/S1516-89132006000700011}.

\bibitem[\citeproctext]{ref-renhornGrowthVitalityEpiphytic1997}
Renhorn, Karl-Erik, Per-Anders Esseen, Kristin Palmqvist, and Bodil
Sundberg. 1997. {``Growth and {Vitality} of {Epiphytic} {Lichens}. {I}.
{Responses} to {Microclimate} Along a {Forest} {Edge}-{Interior}
{Gradient}.''} \emph{Oecologia} 109 (1): 1--9.
\url{http://www.jstor.org/stable/4221485}.

\bibitem[\citeproctext]{ref-reynosoHerbivoryDamageOak2007}
Reynoso, Juan Antonio, and Guadalupe Williams-Linera. 2007. {``Herbivory
Damage on Oak Seedlings at the Edge of Cloud Forest Fragments.''}
\emph{Botanical Sciences}, no. 80 (June): 29--34.
\url{https://doi.org/10.17129/botsci.1743}.

\bibitem[\citeproctext]{ref-santos-barreraRoleMatrixedgeDynamics2011}
Santos-Barrera, Georgina, and Nicolás Urbina-Cardona. 2011. {``The Role
of the Matrix-Edge Dynamics of Amphibian Conservation in Tropical
Montane Fragmented Landscapes.''} \emph{Revista Mexicana de
Biodiversidad} 82 (2).
\url{https://doi.org/10.22201/ib.20078706e.2011.2.463}.

\bibitem[\citeproctext]{ref-savilaaksoMicroclimateTreeCommunity2009}
Savilaakso, Sini, Jenny Koivisto, Timo O. Veteli, and Heikki Roininen.
2009. {``Microclimate and {Tree} {Community} {Linked} to {Differences}
in {Lepidopteran} {Larval} {Communities} Between {Forest} {Fragments}
and {Continuous} {Forest}.''} \emph{Diversity and Distributions} 15 (2):
356--65. \url{http://www.jstor.org/stable/20532103}.

\bibitem[\citeproctext]{ref-silvaComparacaoEntreParametros2010}
Silva, Valéria Teodoro Da, Paulo Souza Medri, Talita Parpinelli
Ferracin, Edmilson Bianchini, José Marcelo Domingues Torezan, and José
Antonio Pimenta. 2010. {``Comparação Entre Parâmetros Abióticos e a
Estrutura Florestal de Um Fragmento de Floresta e Um Reflorestamento
Abandonado de Eucalipto ({Eucalyptus} Saligna {Smith}) No Parque
Ecológico Da {Klabin}, {Telêmaco} {Borba}/{PR}.''} \emph{Semina:
Ciências Biológicas e Da Saúde} 31 (1): 37.
\url{https://doi.org/10.5433/1679-0367.2010v31n1p37}.

\bibitem[\citeproctext]{ref-desiqueiraUSINGVARIANCESMICROCLIMATE}
Siqueira, Ludmila P de, Mário Basílio de Matos, Dalva M Silva Matos,
Maria Isabel G Braz, and Leonardo Silva-Lima. n.d. {``{USING} {THE}
{VARIANCES} {OF} {MICROCLIMATE} {VARIABLES} {TO} {DETERMINE} {EDGE}
{EFFECTS} {IN} {SMALL} {ATLANTIC} {RAIN} {FOREST} {FRAGMENTS},
{SOUTH}-{EASTERN} {BRAZIL}.''}

\bibitem[\citeproctext]{ref-sizerResponsesWoodyPlant1999}
Sizer, Nigel, and Edmund V. J. Tanner. 1999. {``Responses of Woody Plant
Seedlings to Edge Formation in a Lowland Tropical Rainforest,
{Amazonia}.''} \emph{Biological Conservation} 91 (2-3): 135--42.
\url{https://doi.org/10.1016/S0006-3207(99)00076-2}.

\bibitem[\citeproctext]{ref-stevensInfluenceEdgeSmall1998}
Stevens, S. M., and T. P. Husband. 1998. {``The Influence of Edge on
Small Mammals: Evidence from {Brazilian} {Atlantic} Forest Fragments.''}
\emph{Biological Conservation} 85 (1-2): 1--8.
\url{https://doi.org/10.1016/S0006-3207(98)00003-2}.

\bibitem[\citeproctext]{ref-031051937}
Turton, S. M., and H. J. Freiburger. 1997. {``Edge and Aspect Effects on
the Microclimate of a Small Tropical Forest Remnant on the {Atherton}
{Tableland}, Northeastern {Australia}.''} \emph{Laurance, W F,
Bierregaard, R O, Jr Tropical Forest Remnants Ecology, Management, and
Conservation of Fragmented Communities}, 45--54.
\url{https://eurekamag.com/research/031/051/031051937.php}.

\bibitem[\citeproctext]{ref-urbina-cardonaHerpetofaunaDiversityMicroenvironment2006}
Urbina-Cardona, J. Nicolás, Mario Olivares-Pérez, and Víctor Hugo
Reynoso. 2006. {``Herpetofauna Diversity and Microenvironment Correlates
Across a Pasture--Edge--Interior Ecotone in Tropical Rainforest
Fragments in the {Los} {Tuxtlas} {Biosphere} {Reserve} of {Veracruz},
{Mexico}.''} \emph{Biological Conservation} 132 (1): 61--75.
\url{https://doi.org/10.1016/j.biocon.2006.03.014}.

\bibitem[\citeproctext]{ref-vanwilgenburgPatternsArthropodAbundance2001}
Van Wilgenburg, Steve L., Daniel F. Mazerolle, and Keith A. Hobson.
2001. {``Patterns of Arthropod Abundance, Vegetation, and Microclimate
at Boreal Forest Edge and Interior in Two Landscapes: {Implications} for
Forest Birds.''} \emph{Écoscience} 8 (4): 454--61.
\url{https://doi.org/10.1080/11956860.2001.11682675}.

\bibitem[\citeproctext]{ref-wattsHydrologyFireRegulate2015}
Watts, Adam C., and Leda N. Kobziar. 2015. {``Hydrology and Fire
Regulate Edge Influence on Microclimate in Wetland Forest Patches.''}
\emph{Freshwater Science} 34 (4): 1383--93.
\url{https://doi.org/10.1086/683534}.

\bibitem[\citeproctext]{ref-williams-lineraMicroenvironmentFloristicsDifferent1998}
Williams-Linera, G., V. Domínguez-Gastelú, and M. E. García-Zurita.
1998. {``Microenvironment and {Floristics} of {Different} {Edges} in a
{Fragmented} {Tropical} {Rainforest}.''} \emph{Conservation Biology} 12
(5): 1091--1102. \url{http://www.jstor.org/stable/2387582}.

\bibitem[\citeproctext]{ref-williams-lineraVegetationStructureEnvironmental1990}
Williams-Linera, Guadalupe. 1990. {``Vegetation {Structure} and
{Environmental} {Conditions} of {Forest} {Edges} in {Panama}.''}
\emph{The Journal of Ecology} 78 (2): 356.
\url{https://doi.org/10.2307/2261117}.

\bibitem[\citeproctext]{ref-wrightEdgeMicroclimateTemperate2010}
Wright, Thomas E., Sabine Kasel, Michael Tausz, and Lauren T. Bennett.
2010. {``Edge Microclimate of Temperate Woodlands as Affected by
Adjoining Land Use.''} \emph{Agricultural and Forest Meteorology} 150
(7-8): 1138--46. \url{https://doi.org/10.1016/j.agrformet.2010.04.016}.

\bibitem[\citeproctext]{ref-ylisirnioWoodlandKeyHabitats2016}
Ylisirniö, Anna-Liisa, Mikko Mönkkönen, Ville Hallikainen, Taina
Ranta-Maunus, and Jari Kouki. 2016. {``Woodland Key Habitats in
Preserving Polypore Diversity in Boreal Forests: {Effects} of Patch
Size, Stand Structure and Microclimate.''} \emph{Forest Ecology and
Management} 373 (August): 138--48.
\url{https://doi.org/10.1016/j.foreco.2016.04.042}.

\bibitem[\citeproctext]{ref-youngMicroclimateVegetationEdge1994}
Young, Andrew, and Neil Mitchell. 1994. {``Microclimate and Vegetation
Edge Effects in a Fragmented Podocarp-Broadleaf Forest in {New}
{Zealand}.''} \emph{Biological Conservation} 67 (1): 63--72.
\url{https://doi.org/10.1016/0006-3207(94)90010-8}.

\end{CSLReferences}

\end{document}
