% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
  12pt,
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot{}
\fancyhead[L]{APCs and Author Diversity (Supplement)}
\fancyhead[R]{p. \thepage}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{caption}
\DeclareCaptionLabelFormat{Sformat}{#1 S#2}
\captionsetup[table]{labelformat=Sformat}
\captionsetup[figure]{labelformat=Sformat}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Piublication Updates Since Review},
  pdfauthor={\_\_\_\_\_ and E. M. Bruna},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Piublication Updates Since Review}
\author{\_\_\_\_\_ and E. M. Bruna}
\date{}

\begin{document}
\maketitle

The following articles have been published since Simon's Thesis

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-AmazonianSecondaryForests}
{``Amazonian Secondary Forests Are Greatly Reducing Fragmentation and
Edge Exposure in Old-Growth Forests - {IOPscience}.''} n.d. Accessed May
30, 2025.
\url{https://iopscience.iop.org/article/10.1088/1748-9326/ad039e/meta}.

\bibitem[\citeproctext]{ref-andersonWeakEdgeEffects2022}
Anderson, Jake A., Colin J. McClean, Sarah Sim, Nathalie Pettorelli,
Ahmad Jelling, Joseph Tangah, and Jane K. Hill. 2022. {``Weak Edge
Effects on Trees in {Bornean} Rainforest Remnants Bordering Oil Palm.''}
\emph{Biotropica} 54 (4): 921--32.
\url{https://doi.org/10.1111/btp.13115}.

\bibitem[\citeproctext]{ref-arroyo-rodriguezDoesForestFragmentation2017}
Arroyo-Rodríguez, Víctor, Romeo A. Saldaña-Vázquez, Lenore Fahrig, and
Bráulio A. Santos. 2017. {``Does Forest Fragmentation Cause an Increase
in Forest Temperature?''} \emph{Ecological Research} 32 (1): 81--88.
\url{https://doi.org/10.1007/s11284-016-1411-6}.

\bibitem[\citeproctext]{ref-atkinsEffectsForestStructural2023}
Atkins, Jeff W., Alexey Shiklomanov, Kayla C. Mathes, Ben Bond-Lamberty,
and Christopher M. Gough. 2023. {``Effects of Forest Structural and
Compositional Change on Forest Microclimates Across a Gradient of
Disturbance Severity.''} \emph{Agricultural and Forest Meteorology} 339
(August): 109566. \url{https://doi.org/10.1016/j.agrformet.2023.109566}.

\bibitem[\citeproctext]{ref-bauerEdgeEffectsAmazon2024}
Bauer, Luise, Andreas Huth, André Bogdanowski, Michael Müller, and Rico
Fischer. 2024. {``Edge {Effects} in {Amazon} {Forests}: {Integrating}
{Remote} {Sensing} and {Modelling} to {Assess} {Changes} in {Biomass}
and {Productivity}.''} \emph{Remote Sensing} 16 (3): 501.
\url{https://doi.org/10.3390/rs16030501}.

\bibitem[\citeproctext]{ref-bernaschiniMicroclimaticEdgeEffects2021}
Bernaschini, María Laura, María Rosa Rossetti, Graciela Valladares, and
Adriana Salvo. 2021. {``Microclimatic Edge Effects in a Fragmented
Forest: Disentangling the Drivers of Ecological Processes in
Plant-Leafminer-Parasitoid Food Webs.''} \emph{Ecological Entomology} 46
(5): 1047--58. \url{https://doi.org/10.1111/een.13040}.

\bibitem[\citeproctext]{ref-blanchardUAVLidarRevealsThat2023}
Blanchard, Grégoire, Nicolas Barbier, Ghislain Vieilledent, Thomas
Ibanez, Vanessa Hequet, Stéphane McCoy, and Philippe Birnbaum. 2023.
{``{UAV}-{Lidar} Reveals That Canopy Structure Mediates the Influence of
Edge Effects on Forest Diversity, Function and Microclimate.''}
\emph{Journal of Ecology} 111 (7): 1411--27.
\url{https://doi.org/10.1111/1365-2745.14105}.

\bibitem[\citeproctext]{ref-defrenneForestMicroclimatesClimate2021}
De Frenne, Pieter, Jonathan Lenoir, Miska Luoto, Brett R. Scheffers,
Florian Zellweger, Juha Aalto, Michael B. Ashcroft, et al. 2021.
{``Forest Microclimates and Climate Change: {Importance}, Drivers and
Future Research Agenda.''} \emph{Global Change Biology} 27 (11):
2279--97. \url{https://doi.org/10.1111/gcb.15569}.

\bibitem[\citeproctext]{ref-depauwUrbanForestMicroclimates2023}
De Pauw, Karen, Leen Depauw, Kim Calders, Steven Caluwaerts, Sara A. O.
Cousins, Emiel De Lombaerde, Martin Diekmann, et al. 2023. {``Urban
Forest Microclimates Across Temperate {Europe} Are Shaped by Deep Edge
Effects and Forest Structure.''} \emph{Agricultural and Forest
Meteorology} 341 (October): 109632.
\url{https://doi.org/10.1016/j.agrformet.2023.109632}.

\bibitem[\citeproctext]{ref-depauwForestUnderstoreyCommunities2022}
De Pauw, Karen, Pieter Sanczuk, Camille Meeussen, Leen Depauw, Emiel De
Lombaerde, Sanne Govaert, Thomas Vanneste, et al. 2022. {``Forest
Understorey Communities Respond Strongly to Light in Interaction with
Forest Structure, but Not to Microclimate Warming.''} \emph{New
Phytologist} 233 (1): 219--35. \url{https://doi.org/10.1111/nph.17803}.

\bibitem[\citeproctext]{ref-diasStructuralEnvironmentalVariability2021}
Dias, Pb, Lp Gomes, Rm Callegaro, Fa Carvalho, and Hm Dias. 2021.
{``Structural and {Environmental} {Variability} from the {Edge} to the
{Interior} of an {Atlantic} {Forest} {Remnant} in {Brazil}.''}
\emph{Journal of Tropical Forest Science} 33 (3): 308--22.
\url{https://www.jstor.org/stable/27039920}.

\bibitem[\citeproctext]{ref-garveyDivergingPatternsForest2022}
Garvey, Sarah M., Pamela H. Templer, Erin A. Pierce, Andrew B. Reinmann,
and Lucy R. Hutyra. 2022. {``Diverging Patterns at the Forest Edge:
{Soil} Respiration Dynamics of Fragmented Forests in Urban and Rural
Areas.''} \emph{Global Change Biology} 28 (9): 3094--3109.
\url{https://doi.org/10.1111/gcb.16099}.

\bibitem[\citeproctext]{ref-gasperiniEffectsMacroclimateMicroclimate2023}
Gasperini, Cristina. 2023. {``The Effects of Macroclimate and
Microclimate on Soil Seed Banks in Temperate Forests.''} Dissertation,
Ghent University.
\url{http://hdl.handle.net/1854/LU-01HBR5QBZ1YCK0QCNJX8EG7G72}.

\bibitem[\citeproctext]{ref-gilbertMicroclimateComplexitiesTrailing2022}
Gilbert, Neil A., Nicholas M. Anich, Mike Worland, and Benjamin
Zuckerberg. 2022. {``Microclimate Complexities at the Trailing Edge of
the Boreal Forest.''} \emph{Forest Ecology and Management} 524
(November): 120533. \url{https://doi.org/10.1016/j.foreco.2022.120533}.

\bibitem[\citeproctext]{ref-grahamDynamicMicroclimateBoundaries2021}
Graham, Eric A., Mark Hansen, William J. Kaiser, Yeung Lam, Eric Yuen,
and Philip W. Rundel. 2021. {``Dynamic {Microclimate} {Boundaries}
Across a {Sharp} {Tropical} {Rainforest}--{Clearing} {Edge}.''}
\emph{Remote Sensing} 13 (9): 1646.
\url{https://doi.org/10.3390/rs13091646}.

\bibitem[\citeproctext]{ref-grilUsingAirborneLiDAR2023}
Gril, Eva, Marianne Laslier, Emilie Gallet-Moron, Sylvie Durrieu, Fabien
Spicher, Vincent Le Roux, Boris Brasseur, et al. 2023. {``Using Airborne
{LiDAR} to Map Forest Microclimate Temperature Buffering or
Amplification.''} \emph{Remote Sensing of Environment} 298 (December):
113820. \url{https://doi.org/10.1016/j.rse.2023.113820}.

\bibitem[\citeproctext]{ref-hesProjectingFutureForest2024}
Hes, Gabriel, Inne Vanderkelen, Rosie Fisher, Jérôme Chave, Jérôme Ogée,
and Edouard L Davin. 2024. {``Projecting Future Forest Microclimate
Using a Land Surface Model.''} \emph{Environmental Research Letters} 19
(2): 024030. \url{https://doi.org/10.1088/1748-9326/ad1f04}.

\bibitem[\citeproctext]{ref-hovuStrongDifferencesMicroclimate2024}
Ho Vu, Khanh, Gabriella Süle, Bence Kovács, and László Erdős. 2024.
{``Strong Differences in Microclimate Among the Habitats of a
Forest-Steppe Ecosystem.''} \emph{Időjárás} 128 (1): 1--26.
\url{https://doi.org/10.28974/idojaras.2024.1.1}.

\bibitem[\citeproctext]{ref-hofmeisterMicroclimateEdgeEffect2019}
Hofmeister, Jeňýk, Jan Hošek, Marek Brabec, Radomíra Střalková, Pavla
Mýlová, Martin Bouda, Joseph L. Pettit, Miloš Rydval, and Miroslav
Svoboda. 2019. {``Microclimate Edge Effect in Small Fragments of
Temperate Forests in the Context of Climate Change.''} \emph{Forest
Ecology and Management} 448 (September): 48--56.
\url{https://doi.org/10.1016/j.foreco.2019.05.069}.

\bibitem[\citeproctext]{ref-kaasikuPredationmediatedEdgeEffects2022}
Kaasiku, T., R. Rannap, and P. Männil. 2022. {``Predation-Mediated Edge
Effects Reduce Survival of Wader Nests at a Wet Grassland-Forest
Edge.''} \emph{Animal Conservation} 25 (5): 692--703.
\url{https://doi.org/10.1111/acv.12774}.

\bibitem[\citeproctext]{ref-kemppinenMicroclimateImportantPart2024}
Kemppinen, Julia, Jonas J. Lembrechts, Koenraad Van Meerbeek, Jofre
Carnicer, Nathalie Isabelle Chardon, Paul Kardol, Jonathan Lenoir, et
al. 2024. {``Microclimate, an Important Part of Ecology and
Biogeography.''} \emph{Global Ecology and Biogeography} 33 (6): e13834.
\url{https://doi.org/10.1111/geb.13834}.

\bibitem[\citeproctext]{ref-koelemeijerForestEdgeEffects2023}
Koelemeijer, Irena Adia, Johan Ehrlén, Pieter De Frenne, Mari Jönsson,
Peter Berg, and Kristoffer Hylander. 2023. {``Forest Edge Effects on
Moss Growth Are Amplified by Drought.''} \emph{Ecological Applications}
33 (4): e2851. \url{https://doi.org/10.1002/eap.2851}.

\bibitem[\citeproctext]{ref-koelemeijerInteractiveEffectsDrought2022}
Koelemeijer, Irena A., Johan Ehrlén, Mari Jönsson, Pieter De Frenne,
Peter Berg, Jenny Andersson, Henrik Weibull, and Kristoffer Hylander.
2022. {``Interactive Effects of Drought and Edge Exposure on Old-Growth
Forest Understory Species.''} \emph{Landscape Ecology} 37 (7): 1839--53.
\url{https://doi.org/10.1007/s10980-022-01441-9}.

\bibitem[\citeproctext]{ref-meeussenMicroclimaticEdgetointeriorGradients2021}
Meeussen, Camille, Sanne Govaert, Thomas Vanneste, Kurt Bollmann, Jörg
Brunet, Kim Calders, Sara A. O. Cousins, et al. 2021. {``Microclimatic
Edge-to-Interior Gradients of {European} Deciduous Forests.''}
\emph{Agricultural and Forest Meteorology} 311 (December): 108699.
\url{https://doi.org/10.1016/j.agrformet.2021.108699}.

\bibitem[\citeproctext]{ref-meza-elizaldeEdgeInfluenceMicroclimate2021}
Meza-Elizalde, María C., and Dolors Armenteras-Pascual. 2021. {``Edge
Influence on the Microclimate and Vegetation of Fragments of a North
{Amazonian} Forest.''} \emph{Forest Ecology and Management} 498
(October): 119546. \url{https://doi.org/10.1016/j.foreco.2021.119546}.

\bibitem[\citeproctext]{ref-morrealeElevatedGrowthBiomass2021}
Morreale, Luca L., Jonathan R. Thompson, Xiaojing Tang, Andrew B.
Reinmann, and Lucy R. Hutyra. 2021. {``Elevated Growth and Biomass Along
Temperate Forest Edges.''} \emph{Nature Communications} 12 (1): 7181.
\url{https://doi.org/10.1038/s41467-021-27373-7}.

\bibitem[\citeproctext]{ref-nunesEdgeEffectsTree2023}
Nunes, Matheus Henrique, Marcel Caritá Vaz, José Luís Campana Camargo,
William F. Laurance, Ana de Andrade, Alberto Vicentini, Susan Laurance,
et al. 2023. {``Edge Effects on Tree Architecture Exacerbate Biomass
Loss of Fragmented {Amazonian} Forests.''} \emph{Nature Communications}
14 (1): 8129. \url{https://doi.org/10.1038/s41467-023-44004-5}.

\bibitem[\citeproctext]{ref-permanaSustainingRainforestRemnants2022}
Permana, Genta, Siti Nurleily Marliana, Ratna Susandarini, and Hadi
Addaha. 2022. {``Sustaining Rainforest Remnants in Plantation
Landscapes: Degree of Oil Palm Stand-Induced Edge Effects on Forest
Microclimate and Regeneration.''} \emph{CERNE} 28: e103039.
\url{https://doi.org/10.1590/01047760202228013039}.

\bibitem[\citeproctext]{ref-schedlbauerEdgeEffectsIncrease2022}
Schedlbauer, Jessica L., and Jason Miller. 2022. {``Edge Effects
Increase Soil Respiration Without Altering Soil Carbon Stocks in
Temperate Broadleaf Forests.''} \emph{Ecosphere} 13 (6): e4092.
\url{https://doi.org/10.1002/ecs2.4092}.

\bibitem[\citeproctext]{ref-schreierMathematicalModellingApproach2022}
Schreier, Amy L., Kristofor A. Voss, and Laura M. Bolt. 2022. {``A
{Mathematical} {Modelling} {Approach} to {Functionally} {Defining}
{Forest} {Edge} and {Its} {Utility} for {Primate} {Behavioural} {Edge}
{Effects}.''} \emph{International Journal of Primatology} 43 (3):
460--79. \url{https://doi.org/10.1007/s10764-022-00289-9}.

\bibitem[\citeproctext]{ref-senevirathnaRemnantForestPatches2024}
Senevirathna, Ayesha D., Hiran H. E. Jayaweera, H. A. S. Gayan
Dharmarathne, and Mayuri R. Wijesinghe. 2024. {``Do Remnant Forest
Patches Provide Microclimate Buffering? {A} Case Study from {Sri}
{Lanka}.''} \emph{Forest Ecology and Management} 562 (June): 121925.
\url{https://doi.org/10.1016/j.foreco.2024.121925}.

\bibitem[\citeproctext]{ref-slaterLivingEdgeForest2024}
Slater, Helen D., Phillipa K. Gillingham, Victoria Pratt, Ben Eaton,
Simon Fletcher, Abdullah Abdullah, Supriadi, and Amanda H. Korstjens.
2024. {``Living on the Edge: Forest Edge Effects on Microclimate and
Terrestrial Mammal Activity in Disturbed Lowland Forest in {Sumatra},
{Indonesia}.''} \emph{Oryx} 58 (2): 228--39.
\url{https://doi.org/10.1017/S0030605323000212}.

\bibitem[\citeproctext]{ref-willmerGlobalImpactsEdge2022}
Willmer, Julian Nicholas G., Thomas Püttker, and Jayme Augusto
Prevedello. 2022. {``Global Impacts of Edge Effects on Species
Richness.''} \emph{Biological Conservation} 272 (August): 109654.
\url{https://doi.org/10.1016/j.biocon.2022.109654}.

\bibitem[\citeproctext]{ref-zellwegerMicroclimateMappingUsing2024}
Zellweger, Florian, Eric Sulmoni, Johanna T. Malle, Andri Baltensweiler,
Tobias Jonas, Niklaus E. Zimmermann, Christian Ginzler, et al. 2024.
{``Microclimate Mapping Using Novel Radiative Transfer Modelling.''}
\emph{Biogeosciences} 21 (2): 605--23.
\url{https://doi.org/10.5194/bg-21-605-2024}.

\bibitem[\citeproctext]{ref-zhengDisentanglingBioticAbiotic2021}
Zheng, Shilu, Bruce L. Webber, Raphael K. Didham, Chun Chen, and
Mingjian Yu. 2021. {``Disentangling Biotic and Abiotic Drivers of
Intraspecific Trait Variation in Woody Plant Seedlings at Forest
Edges.''} \emph{Ecology and Evolution} 11 (14): 9728--40.
\url{https://doi.org/10.1002/ece3.7799}.

\end{CSLReferences}

\end{document}
